Covariate analysis of ROSMAP reprocessed counts (with CQN normalisation and covariates adjusted)

### 2017-04-14 code/Rmd/ROSMAP_REPROCESSED.Rmd
Minor sanity changes

# Estimate surrogate variables
SURR.VAR = sva::sva(CQN.GENE_EXPRESSION$y+CQN.GENE_EXPRESSION$offset, 
                    MODEL1, MODEL0, n.sv = NUM.SV, B = 3)$sv
SURR.VAR = data.frame(SURR.VAR)

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Set annotations
all.annotations = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay	 = 'Reprocessed RNAseq',

@@

# Store differential expression results
write.table(DE, file = 'ROSMAP_DLPFC_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('ROSMAP_DLPFC_DiffExpression.tsv', name = 'Differential Expression Results (cogdx)', 
                parentId = CODE$properties$id)
annotations(DEXP_OBJ) = annotations(CODE)
annotations(DEXP_OBJ)$dataSubType = 'diffExp'
DEXP_OBJ = synStore(DEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
stopCluster(cl)
```
|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |
|  Design Matrix                              |  `r DM_OBJ$properties$id`        |
|  Surrogate Variables                        |  `r SURR_OBJ$properties$id`      |
|  Residual Expression (for eQTL)             |  `r eEXP_OBJ$properties$id`      |
|  Residual Expression (for network analysis) |  `r nEXP_OBJ$properties$id`      |
|  Differential Expression                    |  `r DEXP_OBJ$properties$id`      |

>>>>

# Estimate surrogate variables
SURR.VAR = sva::sva(CQN.GENE_EXPRESSION$y+CQN.GENE_EXPRESSION$offset, 
                    MODEL1, MODEL0, n.sv = NUM.SV, B = 30)$sv
SURR.VAR = data.frame(SURR.VAR)

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Set annotations
all.annotations = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay	 = 'RNAseq',
  assaySubType = 'Reprocessed',

@@

# Store differential expression results
rbindlist(all.diff.exp, use.names = T, fill = T) %>%
  write.table(file = 'ROSMAP_DLPFC_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('ROSMAP_DLPFC_DiffExpression.tsv', name = 'Differential Expression Results (cogdx)', 
                parentId = CODE$properties$id)
annotations(DEXP_OBJ) = annotations(CODE)
annotations(DEXP_OBJ)$dataSubType = 'diffExp'
DEXP_OBJ = synStore(DEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
stopCluster(cl)
```
|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |
|  Design Matrix                              |  `r DM_OBJ$properties$id`        |
|  Surrogate Variables                        |  `r SURR_OBJ$properties$id`      |
|  Residual Expression (for eQTL)             |  `r eEXP_OBJ$properties$id`      |
|  Residual Expression (for network analysis) |  `r nEXP_OBJ$properties$id`      |
|  Differential Expression                    |  `r DEXP_OBJ$properties$id`      |
